\documentclass{report}
\usepackage{xcolor}
\usepackage[a4paper,  total={185mm,260mm},
 left=10mm,
 top=20mm]{geometry}
\usepackage{tikz}
\usepackage{graphicx}
\usepackage{svg}
\usepackage{minted}
\usepackage{moresize}
\usepackage{nth}
\usepackage{lmodern}
\usepackage{relsize}
\usepackage{hyperref}
\usepackage{biblatex}
\usepackage[most]{tcolorbox}
\addbibresource{refs.bib}

% \begin{definitionbox}{term}
%	... the term's definition ...
% \end{definitionbox}
\newtcolorbox[auto counter,number within=section]{definitionbox}[2][]{%
	colback=black!5!white,colframe=black,arc=0mm,sharp corners=all,fonttitle=\bfseries,%
	title=#2}

% \begin{prosbox}
%	... the term's definition ...
% \end{prosbox}
\newtcolorbox[]{prosbox}[1][]{%
	colback=green!5!white,breakable,colframe=green!75!black,leftrule=3mm,arc=0mm,sharp corners=all, #1}
 
% \begin{prosbox}
%	... the term's definition ...
% \end{prosbox}
\newtcolorbox[]{consbox}[1][]{%
	colback=red!5!white,breakable,colframe=red!75!black,leftrule=3mm,arc=0mm,sharp corners=all, #1}

\begin{document}

\include{titlepage/main}

\begin{abstract}
    Embedded databases allow developers to easily embed a data store within an
    application while providing a convenient query interface. For many
    applications, the schema of the data store is static, and the set of
    parameterized queries is known at application compile time.
    \\
    \\ No existing embedded databases take advantage of this knowledge for
    logical optimisation. The goal of this project is to build one that does.
    \\
    \\ The main outcome of this project is \textit{emdb}: a prototype embedded
    database compiler that generates the optimised code for a data store from a
    schema and queries.
\end{abstract}

\renewcommand{\abstractname}{Acknowledgements}
\begin{abstract}
    I would like to thank my suprvisor, Dr. Holger Pirk, for his willingness to
    supervise my wild idea, and for his teaching of the data processing module
    that inspired it.
    \\
    \\ I would also like to thank my friends, family, neighbours, Imperial College,
    and God for their support.
    \\
    \\ Finally I would like to thank the general population for not implementing what appears to be a
    no-brainer solution to improving the usability \& performance of embedded databases, and leaving it
    open for this \& future individual projects.
\end{abstract}


\tableofcontents
% \listoffigures
% \listoftables

\newpage

\input{introduction/main}
\input{background/main}
\input{project_plan/main}
\input{evaluation_plan/main}

\printbibliography

\end{document}
